What We Eval in the Shadows

### 2021-08-13 paper/main.tex
Fix indetantion of code in 6
Update 6.shadowing

\paragraph{Shadowing}
%%% TODO ?????????????////
Many packages use \eval to implement variations of the \k{base} R functions.
For example, the \k{igraph} package provides the \k{do_call} function
shown below. This is a variant of the \k{do.call} function from the
\k{base} package. This function executes a function call by constructs it
from a name and a list of arguments and calling \eval.

>>>>

\paragraph{Shadowing}
%%% TODO ?????????????////
Many packages use \eval to implement variations of the \k{base} R functions.
For example, the \k{igraph} package provides the \k{do_call} function shown
below. This is a variant of the builtin \k{do.call} function with the
additional support for specifying the environment where the call should happen.
It constructs a call from a name and a list of arguments, and pass it to \eval.
